---
title: Capturing Benefish4 in Data
subtitle: Draft write up
author: James Hogan, FAME - SPC
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
   bookdown::word_document2:
      reference_docx: "C:/From BigDisk/GIT/Benefish_Data_Collection/Product_Output/SPC_R_Template.docx"
      toc: true  
      number_sections: false   
header-includes:
   - \usepackage[percent]{overpic}   
   - \usepackage{tikz}
   - \usetikzlibrary{calc}
   - \usepackage{graphicx}
   - \usepackage{placeins}
   - \usepackage{dcolumn}
   - \usepackage{fancyhdr}
   - \pagestyle{fancy}
   - \fancyhf{}
   - \addtolength{\headwidth}{\marginparsep}
   - \addtolength{\headwidth}{\marginparwidth}   

references:
- id: Benefish4
  title: Fisheries in the economies of Pacific Island countries and territories (Benefish Study 4)
  author: 
   - family: Gillett 
     given: R
   - family: Fong
     given: M
  URL: 'https:// purl.org/spc/digilib/doc/ppizh'
  publisher: The Pacific Community 
  issued:
    year: 2023
---
\newpage


```{r setup, cache=FALSE, include=FALSE}

   ##
   ##    Core libraries
   ##
      library(ggplot2)
      library(plyr)
      library(stringr)
      library(reshape2)
      library(lubridate)
      library(calibrate)
      library(Hmisc)
      library(RColorBrewer)
      library(stringi)
      library(sqldf)
      library(scales)
      library(RDCOMClient)
      library(extrafont)
      library(tictoc)
   ##
   ##    Project-specific libraries
   ##
      library(data.table)

      library(knitr)
      library(htmlTable)
      library(png)
      library(bookdown)
      library(kableExtra)
      library(pander)
      library(officer)
      library(stargazer)
##
##    Grab the reporting datasets
##
   load("C:/From BigDisk/GIT/Benefish_Data_Collection/Data_Output/Final_Cleaned_Benefish4_Data.rda")
   load("C:/From BigDisk/GIT/Benefish_Data_Collection/Data_Intermediate/Cleaned_Data.rda")
   load("C:/From BigDisk/GIT/Benefish_Data_Collection/Data_Intermediate/All_Tables.rda")
   load("C:/From BigDisk/GIT/Benefish_Data_Collection/Data_Intermediate/Cleaned_Table_Names.rda")
   load("C:/From BigDisk/GIT/Benefish_Data_Collection/Data_Intermediate/Together.rda")
   load("C:/From BigDisk/GIT/Benefish_Data_Collection/Data_Output/Exchange_Rates.rda")

   ##
   ##    These data frames were made from Make_Pictures_And_Check.r for reporting purposes
   ##
   load("C:/From BigDisk/GIT/Benefish_Data_Collection/Data_Intermediate/Table_Aggregate_Values.rda")
   load("C:/From BigDisk/GIT/Benefish_Data_Collection/Data_Intermediate/Table_Aggregate_Volumes.rda")
   load("C:/From BigDisk/GIT/Benefish_Data_Collection/Data_Intermediate/Table_Aquiculture.rda")


   ##
   ##    Grab the FFA's data
   ##
   load("C:/From BigDisk/GIT/COMTRADE/Data_Output/FFA_Core_Tuna.rda")
   load("C:/From BigDisk/GIT/COMTRADE/Data_Intermediate/FFA_Compendium_of_Economic_and_Development_Statistics_2022.rda")

   
   
   options(xtable.comment = FALSE)

   BaseDir <- "C:/From BigDisk/GIT/Benefish_Data_Collection/Graphical_Output/"
   
   Together <- Together[order(Together$In_Captured, Together$Standardised_Table_Name, Together$Country, Together$BeneFish_Table_Name),]
   Together$Table <- str_replace_all(Together$Table,"'","")
   
   Together$BeneFish_Table_Name <- str_replace_all(Together$BeneFish_Table_Name,"\x92","")
   Together$BeneFish_Table_Name <- str_replace_all(Together$BeneFish_Table_Name,"\\%","")
   Together$BeneFish_Table_Name <- str_replace_all(Together$BeneFish_Table_Name,"\\(","")
   Together$BeneFish_Table_Name <- str_replace_all(Together$BeneFish_Table_Name,"\\)","")
   Together$BeneFish_Table_Name <- textclean::replace_non_ascii(Together$BeneFish_Table_Name)
   Together$BeneFish_Table_Name <- str_replace_all(Together$BeneFish_Table_Name,"_"," ")
   Together$BeneFish_Table_Name <- str_replace_all(Together$BeneFish_Table_Name,"_"," ")
   Together$Country <- str_replace_all(Together$Country,"_"," ")
   Together$BeneFish_Table_Name <- str_replace_all(Together$BeneFish_Table_Name,"_"," ")
   
   Together$Standardised_Table_Name <- ifelse(is.na(Together$Standardised_Table_Name) & !is.na(Together$BeneFish_Table_Name), "Duplicate Data", Together$Standardised_Table_Name)
   
   
   ##
   ##    Carve it out, check it out, and make pictures
   ##
      Catches_By_Method         <- data.table(Final_Cleaned_Benefish4_Data[["Catches by Method"]])
      Domestic_Fish_Consumption <- data.table(Final_Cleaned_Benefish4_Data[["Domestic Fish Consumption"]])
      Benefish_studies          <- data.table(Final_Cleaned_Benefish4_Data[["Estimates by the Benefish studies of annual fisheries harvests"]])
      Fish_Exports              <- data.table(Final_Cleaned_Benefish4_Data[["Fish Exports"]])
      Fisheries_Revenue         <- data.table(Final_Cleaned_Benefish4_Data[["Fisheries Revenue"]])
      Fish_GDP                  <- data.table(Final_Cleaned_Benefish4_Data[["Fishing contribution to GDP"]])
      Fish_GDP_Var              <- data.table(Final_Cleaned_Benefish4_Data[["Fishing contribution to GDP - VAR Method"]])
      Fishing_Employment        <- data.table(Final_Cleaned_Benefish4_Data[["Fishing Employment"]])
      Hhld_Fishing              <- data.table(Final_Cleaned_Benefish4_Data[["Number of households engaged in fishing"]])
      Price_Measures            <- data.table(Final_Cleaned_Benefish4_Data[["Price Measures"]])
      Val_of_Prod               <- data.table(Final_Cleaned_Benefish4_Data[["Value of production in 2021"]])
      Vol_of_Prod               <- data.table(Final_Cleaned_Benefish4_Data[["Volume of fishery production by PICT"]])
      Vol_of_Prod2021           <- data.table(Final_Cleaned_Benefish4_Data[["Volume of production in 2021"]])         
   
   

```
[^Compendium]: It was here: https://www.ffa.int/publications-and-statistics/statistics/ but is now not :(
[^authors]: Robert Gillett and Merelesita Fong
[^datapolicy]: https://www.spc.int/digitallibrary/get/o4wf6
[^IDI]: https://www.stats.govt.nz/integrated-data/
[^Admin]: https://www.stats.govt.nz/corporate/cabinet-papers-modernising-and-transforming-the-2028-census-public-consultation-on-an-administrative-data-first-approach-for-census/
[^caseforchange]: https://www.stats.govt.nz/assets/Uploads/Corporate/Cabinet-papers/Modernising-our-approach-to-the-2028-Census/2.Appendix-1_-Modernising-and-transforming-the-approach-to-census.pdf
[^CROP]: https://forumsec.org/council-regional-organisations-pacific-crop

<!-- 
##
##       This bit below is the commentary written in R Markup
--> 

# Overview

_FISHERIES in the ECONOMIES of Pacific Island Countries and Territories_ is a publication involving two consultants[^authors] visiting the fisheries and statistical agencies of 24 Pacific Island Countries and Territories (PICTs) collecting and ground-truthing a myriad of fisheries-related statistics. Ultimately, their work was summarised into a picture of the pacific economy and its change over the 16 years of the publication's series. 

The latest in the series, Benefish4 (@Benefish4) clocks in as a 705-physical page pdf report.

The current piece of work on digitising Benefish4's data is a bit more modest then the Benefish reports sort to achieve. This project's focus has been on extracting as much data from the published pdf report as possible and making the electronic information available for researchers. 


## Adherence to Statistical Standards and Measurement Consistency

This project’s complexity lays in the share volume and breadth of information within the physical report, and the inconsistencies in the different metrics for the same things collected from the PICTs.

A "classifications and standards" approach has been taken to try and retrospectively apply data consistency principles to the metrics and make them as cross-country comparable as possible. For example, significant effort went into making consistent units of measure. Unfortunately, significant variation in some measures, for example within [Fish Exports], has been inevitable because of the nature of the original source material.



## Observations from the Data Extraction Process

The Pacific region's analytical capability has developed in the sixteen years the Benefish reports have been compiled. The growth of reliable pacific internet connectivity, and increased information technology skills within countries and organisations suggest alternative data sources and approaches might be considered for future Benefish-type data collections and reports.

Some suggestions are:

*	Working more formally with Council of Regional Organisations of the Pacific (CROP)  agencies to advance Benefish-type data collections with other organisations;

*	Working more explicitly with SPC’s Statistics for Development Division (SDD), its internal statistical office, and

*	Exploring the value of FAME administrative-collected data sources.

Others include taking a sharper focus on what are the minimum analytical / information "functional requirements" of future reports: what analysis do they need to be able to support, and how are future reports intended to be used, and adjusting the report format and content respectively.

Future reports should consider the scope of what’s being collected, and focus more attention on collecting data from each. The report itself, in “Chapter 36 Recommendations”, reached a similar conclusion.



### Sharpening the Report's Focus

The Benefish publication, as a single report, is too broad to do justice to all the topics inside it. The report's breadth comes at the cost of it being _comprehensive_ on its topics.

Quite simply, the report contains "too much stuff". It collects and reports economics statistics, social statistics, industry statistics; however, none of each area receives an in-depth analytical focus or cross-country analysis it deserves. 



### Cross FFA / SPC Data Collection Processes

Some of the measures in the Benefish4 report are better measured elsewhere across the more broadly defined "Pacific Statistical System". 

For Pacific economies, tuna is a significant source of food nutrition, government revenue and economic production. The Pacific Island's Forum Fisheries Agency's (FFA) mandate to is to help its 17 members manage, control and develop their sustainable offshore fisheries including through facilitating regional cooperation. Not all FFA members are SPC members, but pooling effort between SPC and FFA and working more explicitly together on enduring data collections that better measure the value of fisheries to pacific country economies must be in both organisation's shared interests. 

Already, better statistics are collected through the FFA than within the Benefish reports. For example, the section on [Fisheries Revenue] compares Benefish4's measures to the Forum Fisheries Agency's "FFA Compendium of Economic and Development Statistics 2022.xlsx".[^Compendium] The coverage of the Compendium includes more countries and for a longer timeseries.

The FFA is one of eight CROP members which might be able to better supply alternative Benefish metrics.

 

### Working in with SPC's Statistics for Development Division

SPC's own SDD regularly and frequently engages with pacific island countries National Statistical Offices. Co-ordinating efforts with SDD offers a path for quicker and consistent data collection on some key Benefish metrics.

SDD might be best placed to supply more comprehensive and timely measures of [Fish Exports] and [Fishing contribution to GDP] than are currently collected through Benefish's four-year interval collection and reporting process. SDD's subject matter experts for each of these areas might also be able to provide deeper insight into the changes occurring within each area across the pacific.



### Exploring FAME Administrative Data Sources

Other more fisheries-related measures might be better derived from FAME's administrative data sources; for example, "Catches by Method" might be derived from FAME's Catch and Effort statistics and our coastal data. Currently, FAME's internal data policies are too restrictive for its data to become a source for producing high-quality economic, and fisheries-related statistics for the Pacific.

SPC would need to revisit its "General Policies: Governance of fisheries, aquaculture and marine ecosystem data provided to SPC by its members" policy[^datapolicy]. The policy provides a framework for how SPC handles any fisheries, aquaculture and marine ecosystems related data including the data handling, ownership, security, sharing, integration and dissemination. 


## Next Steps
At the start of this project, the plan was to upload the cleaned Benefish data int SPC's .Stat system. However, after discussions with SDD, the cleaned data might be better suited being uploaded into SPC's Data Hub as the CSV files they're currently existing as. The move from .Stat to the Data Hub recognises the variables within the tables are still quite idiosyncratic for each country source, despite being grouped thematically.

Secondly, more planning around the structure and the content of the next Benefish report is needed, to be able to identify which elements might be replaced with administrative data, which components can come from other sources, like SDD, and which components need a dedicated data collection system developed that supports the on-going collection of data.

\newpage



# Benefish Summary Tables

Of the Benefish tables, the Summary Tables of Tables 29-1, 29-2, 29-7 are the most useful since were designed to enable cross-PICT comparisons to be drawn


### Volume of production in 2021


```{r VolofProd21, echo=FALSE}
   
      ##
      ##    Estimate US$ for non-US$ currencies
      ##
       Print_Me <- data.table::dcast(Vol_of_Prod2021[Vol_of_Prod2021$PICT != "Total",],
                                     PICT ~ Metric,
                                     value.var = "Value")
       Print_Me$`Total (Excl Aquaculture)` <- rowSums(Print_Me[,c("Coastal commercial","Coastal subsistence","Freshwater","Offshore Foreign Based","Offshore Locally Based")])
       
       Print_Me <- Print_Me[order(-Print_Me$`Total (Excl Aquaculture)`),]

       knitr::kable(Print_Me[,c("PICT", "Coastal commercial","Coastal subsistence","Freshwater","Offshore Foreign Based","Offshore Locally Based","Total (Excl Aquaculture)", "Aquaculture - Tonnes", "Aquaculture - Pieces")],
                    format = "markdown",
                    format.args = list(decimal.mark = ".", big.mark = ","),
                    digit = 0,
                    align = c('lrrrrrrrrrr'),
                    booktabs = TRUE,
                    caption= "Volume of Production - 2021")
```

```{r VolofProd21unique, echo=FALSE}
        

       knitr::kable(unique(Vol_of_Prod2021[,c("Member_Country", "Table")]),
                    format = "markdown",
                    format.args = list(decimal.mark = ".", big.mark = ","),
                    digit = 0,
                    align = c('lcr'),
                    booktabs = TRUE,
                    caption= "Benefish Tables contributing to the Volume of Production - 2021 Measure")
        
        
```

\newpage



### Value of production in 2021


```{r ValofProd, echo=FALSE}
   
      ##
      ##    Estimate US$ for non-US$ currencies
      ##
       Print_Me <- data.table::dcast(Val_of_Prod[Val_of_Prod$PICT != "Total",],
                                     PICT ~ Metric,
                                     value.var = "Value")
       Print_Me$Total <- rowSums(Print_Me[,2:length(Print_Me)])
         
       Print_Me <- Print_Me[order(-Print_Me$Total),]

      knitr::kable(Print_Me,
                   format = "markdown",
                   format.args = list(decimal.mark = ".", big.mark = ","),
                   digit = 0,
                   align = c('lrrrrrrrrr'),
                   booktabs = TRUE,
                   caption= "Value of production in 2021 - US$")
        
```

```{r ValofProdunique, echo=FALSE}
        

      knitr::kable(unique(Val_of_Prod[,c("Member_Country", "Table")]),
                   format = "markdown",
                   format.args = list(decimal.mark = ".", big.mark = ","),
                   digit = 0,
                   align = c('lcr'),
                   booktabs = TRUE,
                   caption= "Benefish Tables contributing to the Value of Production in 2021 Measure")
        
        
```



\newpage



### Volume of fishery production by PICT


```{r VolofProd, echo=FALSE}
   
      ##
      ##    Estimate US$ for non-US$ currencies
      ##
       Print_Me <- data.table::dcast(Vol_of_Prod[Vol_of_Prod$PICT != "Total",],
                                     PICT + Year ~ Metric,
                                     value.var = "Value")
       Print_Me$Total <- rowSums(Print_Me[,3:length(Print_Me)])
         
       Print_Me <- Print_Me[order(Print_Me$Year, -Print_Me$Total),]

       knitr::kable(Print_Me,
                    format = "markdown",
                    format.args = list(decimal.mark = ".", big.mark = ","),
                    digit = 0,
                    align = c('lcrrrrrrrrr'),
                    booktabs = TRUE,
                    caption= "Volume of Production - Tonnes")
        
```

```{r VolofProdunique, echo=FALSE}

       knitr::kable(unique(Vol_of_Prod[,c("Member_Country", "Table")]),
                    format = "markdown",
                    format.args = list(decimal.mark = ".", big.mark = ","),
                    digit = 0,
                    align = c('lcr'),
                    booktabs = TRUE,
                    caption= "Benefish Tables contributing to the Volume of Production Measure")
        
        
```



\newpage


# Benefish Detailed Tables


```{r Values, echo=FALSE}

knitr::kable(Table_Aggregate_Values[Table_Aggregate_Values$Year == 2021, c("Member_Country","Coastal commercial","Coastal subsistence","Freshwater","Offshore Foreign Based","Offshore Locally Based","Aquaculture","Total")],
             row.names = FALSE,
             format = "markdown",
             align = c('lrrrrrrr'),
             format.args = list(decimal.mark = ".", big.mark = ","),
             digit = 0,
             booktabs = TRUE,
             caption= "Electronic Benefish4 Fishery Values - 2021")
```


\FloatBarrier



```{r Volumes, echo=FALSE}

knitr::kable(Table_Aggregate_Volumes[Table_Aggregate_Volumes$Year == 2021, c("Member_Country","Coastal commercial","Coastal subsistence","Freshwater","Offshore Foreign Based","Offshore Locally Based","Total Tonnes (excl Aqua)","Aquaculture","Pieces")] ,
             row.names = FALSE,
             format = "markdown",
             align = c('llllllllll'),
             format.args = list(decimal.mark = ".", big.mark = ","),
             digit = 0,
             booktabs = TRUE,
             caption= "Electronic Benefish4 Fishery Volumes - 2021")
             
```

```{r Volumesunique, echo=FALSE}
             
      knitr::kable(unique(Benefish_studies[,c("Member_Country", "Table")]),
                   format = "markdown",
                   format.args = list(decimal.mark = ".", big.mark = ","),
                   digit = 2,
                   align = c('lc'),
                   booktabs = TRUE,
                   caption= "Benefish Tables contributing to Aggregate Value and Volume Metrics")             
             
```


\FloatBarrier


\newpage


## Aquaculture
Gillett, in chapter 35.5, highlighted the scarcity of information about national aquaculture production as a significant finding from the study. One of the most outstanding points about aquaculture in the region – and perhaps one of the most
remarkable observations during the study – was the lack of knowledge of the overall aquaculture production in almost every PICT. Indeed, he felt: "Considering the enormous amount of development funds and public money spent on promotion of
aquaculture in the region, it is amazing that there is so little monitoring of the progress of aquaculture development in terms of the total volume and value of production."

That same lack of confidence in the data is also apparent when the value of aquaculture reconciled against its volume components: tonnes and pieces. The volume and value metrics bear no systematic relationship to each other because, if they did, then techniques like regression analysis or simultaneous equations analysis would estimate a non-negative separate implicit aquaculture prices per tonne and per peice. Attempts to allocate the value to the volumes through estimating an implicit price failed to produce non-negative values, implying that neither the volume nor the value aquaculture measures related to the each other.


```{r AquicultureTable, echo=FALSE}

         knitr::kable(Table_Aquiculture,
                      row.names = FALSE,
                      format = "markdown",
                      format.args = list(decimal.mark = ".", big.mark = ","),
                      digit = 2,
                      align = c('llrrr'),
                      booktabs = TRUE,
                      caption= "Benefish4 Aquiculture Metrics")
             
```

```{r Aquicultureunique, echo=FALSE}
                   
      knitr::kable(unique(Benefish_studies[Harvest_Sector == "Aquaculture",c("Member_Country", "Table")]),
                   format = "markdown",
                   format.args = list(decimal.mark = ".", big.mark = ","),
                   digit = 2,
                   align = c('lc'),
                   booktabs = TRUE,
                   caption= "Benefish Tables contributing to Aquiculture Metrics")
```



```{r SimPrice, echo=FALSE}

    
   ##
   ##    Simultaneous equation to reveal price? Nup - negative prices
   ##
      Reduce <- Table_Aquiculture[,
                          list(`Value (US$)`  = sum(`Value (US$)`, na.rm = TRUE),
                               Tonnes = sum(Tonnes, na.rm = TRUE),
                               Pieces = sum(Pieces, na.rm = TRUE)),
                          key = list(Year = as.numeric(Year))]
                          
      knitr::kable(Reduce,
                   format = "markdown",
                   format.args = list(decimal.mark = ".", big.mark = ","),
                   digit = 2,
                   align = c('lrrr'),
                   booktabs = TRUE,
                   caption= "Aquaculture $US Value, Quantity (tonnes) and number of Pieces")
                   
      names(Reduce)[names(Reduce) == "Value (US$)"] <- "Price"
      
      A <- as.matrix(Reduce[,c(3,4,1)])    
      b <- as.matrix(Reduce[,c(2)]) 
      
#      knitr::kable(solve(A, b),
#                   format = "markdown",
#                   format.args = list(decimal.mark = ".", big.mark = ","),
#                   digit = 2,
#                   align = c('llrrr'),
#                   booktabs = TRUE,
#                   caption= "Estimated Price - 2007,2014,2021")
      
      A <- as.matrix(Reduce[1:2,c(3,4)])     
      b <- as.matrix(Reduce[1:2,c(2)])  
#      knitr::kable(solve(A, b),
#                   format = "markdown",
#                   format.args = list(decimal.mark = ".", big.mark = ","),
#                   digit = 2,
#                   align = c('llrrr'),
#                   booktabs = TRUE,
#                   caption= "Estimated Price - 2007,2021")
      
      A <- as.matrix(Reduce[2:3,c(3,4)])     
      b <- as.matrix(Reduce[2:3,c(2)])  
#     knitr::kable(solve(A, b),
#                   format = "markdown",
#                   format.args = list(decimal.mark = ".", big.mark = ","),
#                   digit = 2,
#                   align = c('llrrr'),
#                   booktabs = TRUE,
#                   caption= "Estimated Price - 2014,2021")
       
      A <- as.matrix(Reduce[c(1,3),c(3,4)])     
      b <- as.matrix(Reduce[c(1,3),c(2)])  
#     knitr::kable(solve(A, b),
#                   format = "markdown",
#                   format.args = list(decimal.mark = ".", big.mark = ","),
#                   digit = 2,
#                   align = c('llrrr'),
#                   booktabs = TRUE,
#                   caption= "Estimated Price - 2007,2021")
       
      OLS <- lm(`Value (US$)` ~ (-1 + Tonnes + Pieces)*Year, Table_Aquiculture)      
          
```


```{r, echo=FALSE, warning=FALSE, message=FALSE}

stargazer::stargazer(OLS, type = "html", title = "Results", out = "C:/From BigDisk/GIT/Benefish_Data_Collection/Data_Output/pp.html")
#shiny::includeHTML("C:/From BigDisk/GIT/Benefish_Data_Collection/Data_Output/pp.html")      
```

\newpage


## Catches by Method



```{r CbyM, echo=FALSE}
   
   ##
   ##    Simultaneous equation to reveal price? Nup - negative prices
   ##
      Reduce <- Catches_By_Method[Unit == "Tonnes",
                          list(Tonnes  = sum(Value, na.rm = TRUE)),
                          key = list(Member_Country,
                                     Year = as.numeric(Year),
                                     Method)]
      Reduce <- data.table::dcast(Reduce,
                                   Member_Country + Year~ Method,
                                   value.var = "Tonnes")
      Reduce <- data.table::melt(Reduce,
                                 id = c("Member_Country","Year"))
                                 
      Reduce$value[is.na(Reduce$value)] <-0

      Reduce <- data.table::dcast(Reduce,
                                   Member_Country + Year ~ variable,
                                   value.var = "value")
        
      knitr::kable(Reduce,
                   format = "markdown",
                   format.args = list(decimal.mark = ".", big.mark = ","),
                   digit = 2,
                   align = c('lrrrr'),
                   booktabs = TRUE,
                   caption= "Catches by Method")
                  
        
```


```{r CbyMUnique, echo=FALSE}
                      
      knitr::kable(unique(Catches_By_Method[,c("Member_Country", "Table")]),
                   format = "markdown",
                   format.args = list(decimal.mark = ".", big.mark = ","),
                   digit = 2,
                   align = c('lc'),
                   booktabs = TRUE,
                   caption= "Benefish Tables contributing to Catches By Method Metrics")
                  
        
```


\newpage

## Domestic Fish Consumption

Domestic fish consumption is a metric with changing collection metrics across countries, significantly complicating cross-country comparisons. Most of the source information for this component resides in the qualitative elements of the Benefish text. For example, the Kiribati domestic fish consumption metrics are encapsulated as twelve bullet points of reference to other studies spanning a range of time periods between 1989 - 2016, with new information included from the 2019/20 Household Income and Expenditure Survey. 

Very little of the fish consumption metrics are quantitative, and where they are (for example below), they are subject to significant cross-country measurement variability.


```{r DFC, echo=FALSE}
   
      Reduce <- Domestic_Fish_Consumption[,
                          list(Value  = sum(Value, na.rm = TRUE)),
                          key = list(Member_Country,
                                     Dimension_Value,
                                     Metric,
                                     Unit)]

        
      knitr::kable(Reduce,
                   format = "markdown",
                   format.args = list(decimal.mark = ".", big.mark = ","),
                   digit = 2,
                   align = c('lrrrr'),
                   booktabs = TRUE,
                   caption= "Domestic Fish Consumption")
        
```


```{r DFCUnique, echo=FALSE}
                            
      knitr::kable(unique(Domestic_Fish_Consumption[,c("Member_Country", "Table")]),
                   format = "markdown",
                   format.args = list(decimal.mark = ".", big.mark = ","),
                   digit = 2,
                   align = c('lc'),
                   booktabs = TRUE,
                   caption= "Benefish Tables contributing to Domestic Fish Consumption Metrics")
                  
        
```


\newpage

## Fish Exports

Fish Exports is another data collection whose metrics are country specific. Table \@ref(tab:FE) below illustrates how the report export dimensions vary by country.


```{r FE, echo=FALSE}
   
      ##
      ##    Estimate US$ for non-US$ currencies
      ##
        
      knitr::kable(unique(Fish_Exports[,c("Member_Country", "Dimension_Value")]),
                   format = "markdown",
                   format.args = list(decimal.mark = ".", big.mark = ","),
                   digit = 2,
                   align = c('lr'),
                   booktabs = TRUE,
                   caption= "Fish Export Dimensions for each Country")
        
```


```{r FEUnique, echo=FALSE}
                   
      knitr::kable(unique(Fish_Exports[,c("Member_Country", "Table")]),
                   format = "markdown",
                   format.args = list(decimal.mark = ".", big.mark = ","),
                   digit = 2,
                   align = c('lc'),
                   booktabs = TRUE,
                   caption= "Benefish Tables contributing to the Fish_Exports Metrics")
        
```


\newpage

## Fisheries Revenue


```{r FR, echo=FALSE}
   
      ##
      ##    Estimate US$ for non-US$ currencies
      ##
         Fisheries_Revenue <- merge(Fisheries_Revenue,
                                   Exchange_Rates,
                                   by.x = c("Unit", "Year"),
                                   by.y = c("Currency", "Year"),
                                   all.x = TRUE)
                              
         Fisheries_Revenue$ToUSDollar <- ifelse(Fisheries_Revenue$Unit == "US$", 1, 
                                          ifelse(Fisheries_Revenue$Unit %in% c("Pieces", "Tonnes"), NA, Fisheries_Revenue$ToUSDollar))
                                   
         Fisheries_Revenue$USDollarEquivalent <- Fisheries_Revenue$Value / Fisheries_Revenue$ToUSDollar
         Fisheries_Revenue <- data.table(Fisheries_Revenue)
         
         Aggregate_Values <- Fisheries_Revenue[!str_detect(Revenue_Source, regex("total", ignore_case = TRUE)),
                                         list(USDollarEquivalent = sum(USDollarEquivalent, na.rm = TRUE)),
                                         keyby = list(Member_Country ,
                                                      Year = as.numeric(Year))]
         Aggregate_Values$Member_Country <- str_replace_all(Aggregate_Values$Member_Country, "_", " ")                                             
      ##
      ##    Bring in the FFA work
      ##
                        
         Together1 <- merge(Aggregate_Values,
                           FFA_Compendium_of_Economic_and_Development_Statistics_2022[FFA_Compendium_of_Economic_and_Development_Statistics_2022$SecondHeading == "Licence and access fee revenue",c("Country", "Year", "Value")],
                           by.x = c("Member_Country", "Year"),
                           by.y = c("Country", "Year"),
                           all  = TRUE)
         Together1$Value <- Together1$Value*1000000
         Together1$Difference <- with(Together1, (USDollarEquivalent - Value))
         names(Together1) <- c("Member_Country","Year","Benefish4","FFA Compendium", "Difference")
         
         Together1$Benefish4[is.na(Together1$Benefish4)] <- 0 
         Together1$`FFA Compendium`[is.na(Together1$`FFA Compendium`)] <- 0 
         Together1$Difference[is.na(Together1$Difference)] <- 0 
         Together1$Year = as.character(Together1$Year)

                        
      knitr::kable(Together1,
                   format = "markdown",
                   format.args = list(decimal.mark = ".", big.mark = ","),
                   digit = 0 ,
                   align = c('lcrrr'),
                   booktabs = TRUE,
                   caption= "Fisheries Revenue for each Country: Benefish4 compared to FFA Compendium")
        
```
                   
```{r FR2, echo=FALSE}
      knitr::kable(unique(Fisheries_Revenue[,c("Member_Country", "Table")]),
                   format = "markdown",
                   format.args = list(decimal.mark = ".", big.mark = ","),
                   digit = 0,
                   align = c('lcr'),
                   booktabs = TRUE,
                   caption= "Benefish Tables contributing to the Fisheries Revenue Metrics")
        
        
```



\newpage

## Fishing contribution to GDP

Fish_GDP

```{r FGDP, echo=FALSE}
   
      ##
      ##    Estimate US$ for non-US$ currencies
      ##
         Fish_GDP <- merge(Fish_GDP,
                           Exchange_Rates,
                           by.x = c("Unit", "Year"),
                           by.y = c("Currency", "Year"),
                           all.x = TRUE)
                              
         Fish_GDP$ToUSDollar <- ifelse(Fish_GDP$Unit == "US$", 1, 
                                          ifelse(Fish_GDP$Unit %in% c("Pieces", "Tonnes"), NA, Fish_GDP$ToUSDollar))
                                   
         Fish_GDP$USDollarEquivalent <- Fish_GDP$Value / Fish_GDP$ToUSDollar
         Fish_GDP <- data.table(Fish_GDP)

      knitr::kable(Fish_GDP[,c("Member_Country", "Year", "Harvest_Sector", "USDollarEquivalent")],
                   format = "markdown",
                   format.args = list(decimal.mark = ".", big.mark = ","),
                   digit = 0,
                   align = c('lclr'),
                   booktabs = TRUE,
                   caption= "Benefish Fisheries GDP Metrics")
        
```


```{r FGDPUnique, echo=FALSE}
                    

      knitr::kable(unique(Fish_GDP[,c("Member_Country", "Table")]),
                   format = "markdown",
                   format.args = list(decimal.mark = ".", big.mark = ","),
                   digit = 0,
                   align = c('lcr'),
                   booktabs = TRUE,
                   caption= "Benefish Tables contributing to the Fish GDP Metrics")
        
        
```


\newpage

## Fishing contribution to GDP - VAR Method


```{r FGDPVar, echo=FALSE}
   
      ##
      ##    Estimate US$ for non-US$ currencies
      ##
         Fish_GDP_Var <- merge(Fish_GDP_Var,
                               Exchange_Rates,
                               by.x = c("Unit", "Year"),
                               by.y = c("Currency", "Year"),
                               all.x = TRUE)
                              
         Fish_GDP_Var$ToUSDollar <- ifelse(Fish_GDP_Var$Unit == "US$", 1, 
                                          ifelse(Fish_GDP_Var$Unit %in% c("Pieces", "Tonnes"), NA, Fish_GDP_Var$ToUSDollar))
                                   
         Fish_GDP_Var$USDollarEquivalent <- Fish_GDP_Var$Value / Fish_GDP_Var$ToUSDollar
         Fish_GDP_Var <- data.table(Fish_GDP_Var)

         Fish_GDP_Var2 <- data.table::dcast(Fish_GDP_Var,
                                           Member_Country + Harvest_Sector + Year ~ GDP_Dimension,
                                           value.var = "USDollarEquivalent")


      knitr::kable(Fish_GDP_Var2[,c("Member_Country","Harvest_Sector","Year","Gross Value of Production","Value added")],
                   format = "markdown",
                   format.args = list(decimal.mark = ".", big.mark = ","),
                   digit = 0,
                   align = c('llcrr'),
                   booktabs = TRUE,
                   caption= "Benefish Fisheries GDP (Value Added Ratio Measure)")
        
```


```{r FGDPVarUnique, echo=FALSE}
             

      knitr::kable(unique(Fish_GDP_Var[,c("Member_Country", "Table")]),
                   format = "markdown",
                   format.args = list(decimal.mark = ".", big.mark = ","),
                   digit = 0,
                   align = c('lcr'),
                   booktabs = TRUE,
                   caption= "Benefish Tables contributing to the Fish GDP (Value Added Ratio Measure)")
        
        
```


\newpage

## Fishing Employment


```{r Femp, echo=FALSE}
   
      ##
      ##    Estimate US$ for non-US$ currencies
      ##

      knitr::kable(Fishing_Employment[,c("Member_Country","Year","Dimension_Value","Value")],
                   format = "markdown",
                   format.args = list(decimal.mark = ".", big.mark = ","),
                   digit = 0,
                   align = c('llcrr'),
                   booktabs = TRUE,
                   caption= "Benefish Fishing Employment")
        
```


```{r FempUnique, echo=FALSE}
              

      knitr::kable(unique(Fishing_Employment[,c("Member_Country", "Table")]),
                   format = "markdown",
                   format.args = list(decimal.mark = ".", big.mark = ","),
                   digit = 0,
                   align = c('lcr'),
                   booktabs = TRUE,
                   caption= "Benefish Tables contributing to the Fishing Employment Measure")
        
        
```


\newpage

## Number of households engaged in fishing


```{r households, echo=FALSE}
   
      ##
      ##    Estimate US$ for non-US$ currencies
      ##

      knitr::kable(Hhld_Fishing[,c("Member_Country","Year","Fish_Activity","Location","Value")],
                   format = "markdown",
                   format.args = list(decimal.mark = ".", big.mark = ","),
                   digit = 0,
                   align = c('llcrr'),
                   booktabs = TRUE,
                   caption= "Benefish Households Engaged in Fishing")
        
```


```{r householdsUnique, echo=FALSE}
              
        

      knitr::kable(unique(Hhld_Fishing[,c("Member_Country", "Table")]),
                   format = "markdown",
                   format.args = list(decimal.mark = ".", big.mark = ","),
                   digit = 0,
                   align = c('lcr'),
                   booktabs = TRUE,
                   caption= "Benefish Tables contributing to the Households Engaged in Fishing Measure")
        
        
```



\newpage

## Price Measures

```{r price, echo=FALSE}
   
      ##
      ##    Estimate US$ for non-US$ currencies
      ##

      knitr::kable(Price_Measures[,c("Member_Country","Year","Dimension_Value","Unit","Value")],
                   format = "markdown",
                   format.args = list(decimal.mark = ".", big.mark = ","),
                   digit = 3,
                   align = c('lcllr'),
                   booktabs = TRUE,
                   caption= "Benefish Price Measures")
        
```


```{r priceUnique, echo=FALSE}
              
               

      knitr::kable(unique(Price_Measures[,c("Member_Country", "Table")]),
                   format = "markdown",
                   format.args = list(decimal.mark = ".", big.mark = ","),
                   digit = 0,
                   align = c('lcr'),
                   booktabs = TRUE,
                   caption= "Benefish Tables contributing to the Price Measures Measure")
        
        
```







# Benefish Tables Excluded from Electronic Transformation
Not all of the Benefish4 tables could be collected together. These are tables which were either too idiosyncratic in content, or were replicated elsewhere.

```{r Missed, echo=FALSE}

knitr::kable(Together[is.na(Together$In_Captured),c("Country","Table", "BeneFish_Table_Name")],
             row.names = FALSE,
             format = "markdown",
             align = c('llllll'),
             booktabs = TRUE,
             caption= "Tables that Couldn't be Compared")
             
```


\newpage

# References

